### 2020-04-13 paper/main.tex
new changes

\documentclass{turabian-thesis}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pslatex}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{paralist}
\usepackage[utf8]{inputenc}
\usepackage{multicol} 
\usepackage[hidelinks]{hyperref}
\usepackage{nameref}
\usepackage{setspace}
\usepackage{listings}

@@

@@

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{claim}{Claim}
\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}

\newcounter{case}[section]
\newenvironment{case}[1][]{\refstepcounter{case}\par\medskip
   \textbf{Case~\thecase. #1} \rmfamily}{\medskip}

\newcounter{subcase}[case]
\newenvironment{subcase}[1][]{\refstepcounter{subcase}\par\medskip
   \textbf{Case~\thecase.\thesubcase. #1} \rmfamily}{\medskip}

@@

   \textbf{Hybrid Model for Interpretable Time Series Analysis}

@@

\chapter*{Abstract}

@@

\addcontentsline{toc}{chapter}{Abstract}
\chapter{Acknowledgments}

@@

\tableofcontents
\listoffigures

\mainmatter
\chapter{Introduction}
\label{chap:introduction}

@@

% \section{The need for interpretable models in management problems}
% The growth of mobile devices and demand for wireless data has created a need for igh quality spectrum sensing and adaptation to improve spectral allocation and interference mitigation is an important route by which we may achieve this.  however have been constrained to relatively specialized solutions which lack the generality needed to deal with a complex and growing number emitter types, interference types and propagation environments.
% This is a significant challenge in the community as expert systems designed to perform well on specialized tasks often lack flexibility and can be expensive and tedious to develop analytically.
\chapter{Related Work}
\label{chap:relatedwork}

@@

\chapter{Data}

@@

\chapter{Preprocessing}
\label{chap:preprocessing}

@@

\chapter{Models}
\label{chap:models}

@@

\chapter{Markov Transition Fields}
\label{chap:mtf}

@@

\chapter{Main Results}
\label{chap:results}

@@

\chapter{Conclusion}
\label{chap:conclusion}
Throughout this thesis, we have stressed the importance of a hybrid machine learning algorithm as well as provided a framework that can successfully classify and visualize different classes when applied to time-series data.

>>>>

\documentclass{turabian-thesis}[12pt]

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pslatex}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{paralist}
\usepackage[utf8]{inputenc}
\usepackage{multicol} 
\usepackage[hidelinks]{hyperref}
\usepackage{nameref}
\usepackage{setspace}
\usepackage{listings}
\usepackage{mathptmx}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\l@section}
  {\hfil}
  {\leaders\hbox{\normalfont$\m@th\mkern \@dotsep mu\hbox{.}\mkern \@dotsep mu$}\hfill}
  {}{}
\makeatother
\usepackage[english]{babel}
\usepackage[font=bf, figurename=FIGURE, labelsep=period]{caption}

\addto\captionsenglish{% Replace "english" with the language you use
  \renewcommand{\contentsname}%
    {TABLE OF CONTENTS}%
}
\usepackage{titlesec}

% \usepackage{tocloft}
% \renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

\usepackage{tocbibind}
\usepackage[titles]{tocloft}
 \renewcommand \cftchapdotsep{1.5}

 \renewcommand{\cfttoctitlefont}{\normalfont\Large}% Remove \bfseries from ToC title
 \renewcommand{\cftsecfont}{}% Remove \bfseries from section titles in ToC
 \renewcommand{\cftsecpagefont}{}% Remove \bfseries from section titles' page in ToC

\let\chaptername\relax

\renewcommand{\cftchapnumwidth}{6em}

\addto{\captionsenglish}{\renewcommand{\bibname}{REFERENCES}}

\addto\captionsenglish{\renewcommand{\chaptername}{CHAPTER}}

@@

% 1 inch margin
\usepackage[margin=1in]{geometry}

@@

\usepackage{fancyhdr}
\fancypagestyle{headings}{%
\cfoot{\thepage}
}
\pagestyle{headings}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}

@@

   \textbf{HYBRID MODEL FOR INTERPRETABLE TIME SERIES ANALYSIS}

@@

\chapter*{ABSTRACT}

@@

\addcontentsline{toc}{chapter}{ABSTRACT}
\chapter{ACKNOWLEDGMENTS}

@@

\newpage
% {\let\bfseries\mdseries% ...or \let\bfseries\relax
\tableofcontents
% }
\newpage

\renewcommand{\listfigurename}{LIST OF FIGURES}
\listoffigures

\mainmatter
\chapter{INTRODUCTION}
\label{chap:introduction}

@@

% \section{The need for interpretable models in management problems}
% The growth of mobile devices and demand for wireless data has created a need for igh quality spectrum sensing and adaptation to improve spectral allocation and interference mitigation is an important route by which we may achieve this.  however have been constrained to relatively specialized solutions which lack the generality needed to deal with a complex and growing number emitter types, interference types and propagation environments.
% This is a significant challenge in the community as expert systems designed to perform well on specialized tasks often lack flexibility and can be expensive and tedious to develop analytically.
\chapter{RELATED WORK}
\label{chap:relatedwork}

@@

\chapter{DATA}

@@

\chapter{PREPROCESSING}
\label{preprocessing}

@@

\chapter{MODELS}
\label{chap:models}

@@

\chapter{MARKOV TRANSITION FIELDS}
\label{chap:mtf}

@@

\chapter{MAIN RESULTS}
\label{chap:results}

@@

\chapter{CONCLUSION}
\label{chap:conclusion}
Throughout this thesis, we have stressed the importance of a hybrid machine learning algorithm as well as provided a framework that can successfully classify and visualize different classes when applied to time-series data.
